\chapter{}

Einstein's thoughts (building on and reconstructing Newton, the alchemist's thought)
on simultaneity become instructive, as do
the thoughts of modern bankers as they scan
their electronic spread-sheets. For bankers
and physicists meditate on states of simultaneity, relative to those who do not, \emph{cannot}
have access to this distance-insensitive equipment. This is to say bankers enjoy abstract
immortality in relation to the banked, along
with quantum physicists and metaphysicians
and magicians.

For Einstein a number of events can be
considered to be taking place at the same
time, but only in relation to an observor
recording different signals from those events
and timing them with coordinated clocks.
(Compare the delicate timing of an international
arbitrage operation which requires relative speed, or relative simultaneity, and
at the same time requires relative ignorance ---
or relative distance --- on the part of one's opponents.) Everything depends on the observor and the recording instruments and
relative accumulations of knowledge (the instruments being a manifestation of assumptions built into them) and speeds of transmission to determine what looks like simultaneity.

Simultaneity has nothing to do with where
those events are happening (unless you are
being shot at from two directions), but rather
when they are percieved. Perception is a
function of distance and the tools required to
transmit knowledge. A corporation, our
chimera, in the \emph{contemplation} of law, this
society of the anonymous and hidden, an
organic being (more than the sum of activities of individuals and groups), with
stored-up misery-and-energy, lives converted
to credit, may be scattered over a wide
geography and over time. All things in it and
of it and about it may be considered simultaneous from the point of view of an auditor
contemplating this balance sheet.
When the accountant's sheet is computerized, constantly recieving information from all over
the world and interconnected with the product of statistical projections from all over
space and time, then all operations are happening simultaneously, including invested-in future events, since they are handled in the present.

Similarly, it is said that any complex of
genetic material contains the complete history of the organism and all preceding organisms (a genetic archeology, but still
alive). By the proscess of combination and
recombination of its memory elements, amino
acids, etc., since it contains all past, probable, potential and possible organisms, even
pre-organisms; and like the elements of, the
combinatorial rules of, say English (rules
which are derived after the languge is mature), is subject to the same operations, containing all past and future literary works,
even those that Shakespeare forgot to write.
Implicit in all these observational operations
is the notion of the simultaneity-observor of
all genetic and\slash or linguistic, and\slash or monetary
possibility. And thus genetics, if seen as
information, is the rememberance of things
past (all the organic --- and inorganic --- universe, all the realized and unrealized beings,
objects and forces) which generate the organisms which invent various schema of
rembererance, which then remember the complex that recollects it.

But for Einstein there was an upper limit:
the speed of light. The quantum physicists,
introducing indeterminacy, and the intervention of the observor and his instrumentation,
implied that in a certain sense, all
events were in fact simultaneous, regardless
of clocks, for they had distributed Mind into
the universe, a notion Einstein rejected.

Let's take a side trip to paradise and consider time there. What happens before the
beginning, or after the end, is a question to
which Kaballists and gnostics address themselves. This problem has been transmitted
right down into modern times in a new form:
what happened \emph{before} The Beginning, the
Big Bang (itself a construct open to doubt)?

\emph{All} matter, energy, space and time (and
thus all possibility) was contracted into a
dimensionless point (or nothingness) ... so
the mythic tale goes. Infinite mass, for if the
point was suseptible to measurement,
even of the most miniscule kind, then its mass
was less than infinite. If all matter, space,
motion, energy, time --- and potentially, perhaps inevitably, all life --- in the universe was
massed into this dimensionless point, then
there could be no time or space \emph{outside} this
dimensionless, infinite-massed point. Infinitely compressed matter and energy (which
included, potentiality, all life) meant that
there was no one to measure it, not even any
automated measuring tools. So all Mind was
there too. Perfect simultaneity, \emph{but not objective simultaneity}, which, being involved
with signals, distance and time, couldn't be
measured. It was therefore eternal inside the
dimensionless point, a feature of all paradises.

Time is not a term that stands by itself, nor
does any other term: all terms are multireferential, bootstrapping every other term
into the air where it hovers like some plasma, contained away from the apprehension
of most people. But the multi-referentiality
(as well as the breakdown into terms of a
complex of things) indicates the intervention of mind inside the universe. If Mind is
an emanation of that pre-moment --- physical, chemical, biological, monetary, literary,
religious --- it might be possible to \emph{remember}
this paradisical past now, as we \emph{remember},
say, Eden, a lower-level and later paradise. It
is out of logic, the mathematics, the equations --- a form of metaphorical activity --- the
statistical retrojection --- a specialized and
leached-out form of memory --- and the observation of the distribution of matter in space,
and the Red Shift, that we might infer, and remember, the Big Bang.

It is over this Big Bang that modern physicists, ancient priests and shamans, magicians, caballists and communications artists come together.

Given this compulsive activity, this associative, similizing, metaphoric, organizing, disorganizing, ordering, concentrating,
distributing, interventionary, aesthetic activity of humans, and the compulsive nescessity
to lay on one hundred and forty four interpolations where there appears the slightest gap
(indeed to invent gaps) we can also say that
all economic observations contain the purified metaphysical and stored-up simultaneous record of all activity. And we can add
that the genetic material is not only an
information-analogue, but a factory and
clock analogue: the gamete's growing becomes an analogy to the ever repeated evolution, a biological mini-Big Bang.

Since all credit is meaningless unless
linked to an active, perpetually moving
market, linked to people to believe in it and
to the institutions they inhabit, given these
massive flows of \emph{perceptions}, symbols and
signs standing for life, space, factories, and
given the increasing velocities, we have
reached the age of Einsteinianism in business, approaching (as in Dante's Paradiso),
simultaneity \emph{inside} this system and serial,
labrorious time and ageing (the post-paradisical universe) \emph{outside} the system. It is
with the arrival of the computers and highspeed communications, with perpetually
operating, around-the-world-all-time-on-line-markets, time and time-zones,
for some speculators, mean less and less, but are
needed more and more.

The zones, after all, are merely a hangover
of local dawns and sun-settings, a way to
start and end the business day (but at the
same time have reference to eternity). For
those, time becomes a manipulable commensurable, a function of price to be adjusted
seasonally, daily, hourly, minutely to the financial needs of different credit\slash time\slash zone-spanning topologies. Linked-up, high-speed
computers, telexes, with their internal and
communicating velocities, working all the
time to coordinate long and short term messages become like the matching up of different infinities.

Now, it is said, \emph{all} can be linked: financial
markets, factories, laboratory work, electrical grid systems, voice conversations, graphic
displays, on-line-in-real-time accounting
systems, tax structures, banking operations,
brokering, trading programs, games, military and political scenarios, telemedical
diagnostic and treatment-delivery networks,
point-of-sale processors, home banking and
trading, data-retrieval... All change the notion of time and timing. The restlessness of
these unsleeping telematic devices negates
out older senses of time. The movements of
humans, matched up to the \emph{movement of the records of humans and their endeavors}
change the notion of time, timeing and human behavior. Real time begins to dance in
time to telecommunicated computer time;
capital-containing time-movements\slash time-containing capital movements. The human
cycle of production and consumption falls
out of line with the informational cycle of
production and consumption. Life is driven
by these abstractions and fictional populations are more suited to survive at these
speeds than humans. It becomes bizzare
when time becomes not only mensurable,
but something that can be corelated to a set
of logic games.

After the reconstruction, or rememberance
of the Big Bang, time was said to move only
in one direction: \enquote{forward.} An anomoly.
This asymetricality was bothersome. After
all, the universe is electromanichean. Then
it was found, possibly, that for sub-atomic
particles time may be bi-directional, an analogy deduced from the assumed bi-polar nature of charged particles. A question: why
should time only go \enquote{forward,} along a
\enquote{line,} as if trying to move away from, or
perhaps forward into an enormous pool of
pre- or post-existent, paradisical pre-creation.
If there are chronons, positive, forward-moving time-particles, then there should be anti-chronons, negative, backward-moving timeparticles. (Or on the other hand, maybe the
observational equipment, the human, subject to time, could not perceive time any
other way --- except in dreams --- and thus projected this time, operationally, imposing ---
as mind imposes --- a certain order in the universe.)

But, if time is moving forward, and matter
is moving outward, expanding, attenuating,
inflating, then entropic disaster faces us and
preoccupies some small, but influential set
of thinkers. It is astonishing that some far-off
heat-death of the universe should affect this
subset with despair, as if they were faced
with a black and dusty cosmos a mere ten or
twenty years from now. This hints at a religious or at least an ideological sensibility.
The crisis demands reconcentration and reunifiction, these new forms of calculational
and accumulative ideology which permeates
all forms of thought. There is also a peculiar
aspect to this thought, a sort of despair. If the
universe perpetually expands, or if it is
steady-state, or expands and contracts in
cycles, all seems \enquote{purposeless.} Now we are
not merely talking about religious thinking,
but scientists have voiced these concerns.
Purpose, as well as the imposition of order in
all things, is negantropy.

This crisis, this terror of conceptual, informational,
ideological inflation, is seen in finance, physics, cosmology, genetics...
The universe-picture collapses for the physicists. All the functions of esoteric calculation-magic to keep the universe alive emerges
in their logic-compared-to-the-universe. The
banker's loans default, their world system is
threatened with collapse, just as a star, using
its energy too freely, burns out too quickly,
collapsing back on itself into a black hole.
The banker must reschedule or re-time his
loans, or at least reform the calenders of his
debtors ... although he cannot retime his
debtor's lives. For the banker and the physicist, the universe must balance, all things in
it, thus time itself: they must hold their
two-aspected world together. For the banker
it may be nescessary to reschedule or slow
down time.

Can this be accepted by those living
in a debtor --- low-energy, low-mass --- nation,
since the tyranny of their bodies may not
repond to this new schema? They cannot
suspend their bodily functions and await the
paradise of debt payoff or redemption in a
hundred years. Therefore, the bankers must
play games with time, population (genetics)
and space. The physicists and cosmologists
also reschedule time, making statistical projections and retrojections, equating (like the
banker) all time with that contained in
a massified and concentrated microworld
which they can then manipulate with ease.

Operations can be performed with timequanta that distort our sense of what time is.
We can add it; we can subtract it; we can
make it go sideways, crowd centuries into
minutes. How much time was spent by
Dante, going through hell, purgatory and
heaven on that Easter triad of days, 1300:
subjective time inside these three realms as
against objective time outside of it? If time
can be accumulated, can it be sold? Truly
sold as a commodity? Can it be consumed,
metabolized? In some sense, yes. How? Be % TODO be -> by
making it into a commodity; the businessman's trick. Commodity means \enquote{the measured against.} Is time, like other commodities, deliverable? We sell time-sharing. But those are, after all, metaphors. We can sell it
as interest. We sell money, we loan money,
and if we are striving for a profit, time
becomes expressed in interest rates already
embedded in money. All money, all that is
valued, contains time, both the time of its
existence and the time incorporated into it.
But, to buy it is still not to \emph{live} it.

Debt redemption is the redemption of
time-price. (A famous work on slave cliometrics is called \booktitle{Time on The Cross}. After the original time on the cross, came the
journey into another space and the ressurrection.) It is performance in production,
events-to-come-treated as if they had already

happened. Time is delivered from then to
now. Ridiculous? If quarks are confined in
larger particles and cannot be separated, but
nevertheless calculated with as if separated,
why not time? No one has ever seen a free
quark; why not confined chronons? Matching time to value, we monetarize it, but in a
\enquote{confined} manner.

There can be no such thing in our current
financial system as a static pool of money, or
near-money. Since it is restless, it has velocity, and if it has velocity, then it traverses
space --- what is velocity without space --- in a
variety of ways. A meter is now defined in
terms of light travel. It was discovered that a
rigid measuring rod shrunk, and so gained
mass, in the direction of the movement relative to a measuring rod in a slower timeframe. Speeding clocks also slow up in the
direction of velocity. We may also say that money,
in perpetual motion, if massed,
slows up time relative to slower moving
money, or conversely, time inside a massed
and concentrated pool of money slows up as
the velocity of money increases. So now
so many fraction-seconds of light traveled
equals a meter, based on the assumption that
light-travel is a constant in any time-frame.
The same operation applies to money, which
can define space (if not pure space, then at
least real-estate). Increase the velocity (requiring what amounts of energy and investments?) to the speed of light and mass will
begin to become compressed into smaller
and smaller spaces approaching nothingness,
infinite mass, and at the same time will be
relatively eternal. Time, from the point of
view of someone's going slower, appears
longer. Infinity, but relative infinity. Immortality, but relative immortality. And when
the speed of light is transcended (or possibly
when there is enough treasure-energy piled
up) then time might go backwards. We have
arrived at the conditions of the black hole.

If we can talk about dollars per time-unit,
we can now also talk about time-units per
dollar. If we change our rates, we can talk
about more dollars per time-unit and more
time-units per dollar. If inflation takes place,
value drops or dollars per item increases,
and therefore rates increase to compensate.
Or conversely, velocity also contributes to
inflation. By the same token, chronons per
unit can be inflated. Inflation creates time.
We approach immortality.

If this seems like an intellectual game,
without consequence in the real world, we
must consider the effects on people of short
and long-term debt, defaults, accelerated
payments and production, in which the
whole cycle must be speeded up in order to
repay. Either people work faster (and live for
shorter periods of time) for less pay, or fewer
people work at faster rates (aided by the
ghost army embedded in robotics and computers).

The speed of light is the ultimate standard,
the limit, Einstein's \emph{primum mobile}. Since
everything is defined in terms of everything
else, there can be no such thing as a \emph{primum
mobile} other than the one those who set the
standards impose on us. While time is
closely linked to light and the traversal of
space, if we link time to compound iterest
formulae, the parameters change. While we
have been reticent, resistant to play with
time because cycles of hunger, fatigue and
death drain us, it is happening nevertheless,
in our practice. But biological time still lurks
somewhere in our perceptions; yielding to
an artificial immortality terrifies us,
like submitting ourselves to heaven and hell.
It should be remembered that an infinite
amount of money must be spent in order to
become equivalent to an infinite amount of
mass and energy, to an infinite amount of
space, lives, energy, history, time... High
technology, capital intensivity compresses
the mass of commodities. Capitech-intensivity increases its mass-energy-time-velocity
in relation to a slower-moving, starvation world.

All operations that can be performed with
credit also indicates a relative immortality,
for the possessor of the accumulation of
credit possesses a huge accumulation of
stored energy-lives, time, in a very small
space: a great mass, which, because it still
can't be metabolized, must manifest itself in
certain expenditures; cars, houses, military
potlatches, estates, hotel rooms, airplanes,
pomp. This, of course, is reckoning backwards; we are deriving certain laws to explain the insane behavior of the rich. And
yet, a dream persists: of one could only store
enough mass-accumulation, then you can
store, perhaps, enough time in a small enough
space to transcend, or at least reach the
speed of light. The question here is, of
course, \emph{real}, \emph{actual} immortality (for whom
and at what price to everyone else?)

The difficulty lies in any human's being able to \emph{metabolize} an extreme amount of
time, or mass, or energy, or velocity, or convert information (which is also a function of all these terms) to something like flesh ...
convert energy, etc., into usable
energy in an assimilable form. (As Ahab, an
insatiable hunter, desiring a sort of immortality, dreamed of swallowing the power of
the sun concretized in the symbol of the
White Whale, Moby Dick.) Thus, in the abstract and therefore in the real world, the
rich create a vacuum around them by sucking up the abstractions, the information
standing for the energies of the world, which
then siphon off the actual energies of the
universe.

But there is something saving after all. The
real, ultimate constant may not be the speed
of light at all, but \emph{felt duration}, after all, give
or take a little of the average lived life. The
felt duration of people ina different time and
speed frame seems subjectively to be the
same (although no one knows) even though
the person in the fast lane is said to live
aeons longer. It is such calculations that
produce vast masses in time and timer-space,
creating a blind impasse, the existence of the
concept of black holes, out of which no light
or energy escapes... Which yield amusing
stories to frighten and amuse the young, but
does not yield any Magellan's passage to an
India-Paradiso.
