\chapter{}

If the \emph{mythology} of the past is \emph{everpresent},
at least in the \emph{memory} (distant signals presently felt, but not in any order) then it too is
simultaneous even though the event is long
gone. Seen this way, event, and thus time,
and thus life, become merely informational;
that is to say an abstraction that can be
handled in a non-real way with real effects.
This is, after all, what dreams and surrealism
are all about. A financial institution is not
only an information-handling and communicating company these days, but a clock, an
observatory with \enquote{eyes} that see electronic
impulses in which all the events it scans are
simultaneous and fused. It is a dream state.

As we continue to struggle on toward
demonstrating this unified field theory as it
is in practice, we see we have arrived
at a dangerous, earth-devouring system of
thought and illusion. We take the whole
development of modern cosmological and
physical theory to be, at the present time, a
function of the \emph{culture} of modern transnational capital. When a certain level of interconnectedness is reached, what will happen is that the universe's symbolic energy
(affecting real energy systems) will move so
fast that it will burn itself out, explode into a
nova (a cosmological financial-informational
bubble), collapse and compress back into a
black hole... leaving the universe outside
quite the way it was for billions of years.

\emph{It is the logic of this mode of thinking that
produces these wierd and surreal visions.}
Welcome to Laputaland.

In the past, magical systems held the notion that there was a link between the microcosm (what happened in people's minds)
and the macrocosm (what happened in the
universe). The macro affected the micro. If
one had the magical tools, then the micro
could affect the macro. Electrical levers were
substituted for magical levers. But the dream
of \emph{magical} control has never been exorcised.
We are still caught in a quasi-metaphysical
system; one that expends enormous resources
and money. It is this dream of intellectual
magic that drives the present information
revolution: the grasp for power and control.
The thought of a small sub-set of the world's
population devastates the earth. Perhaps,
after all, modern capitalism is a great factory
for the production of angels.

Illusion dominates. It doesn't matter yet
since the information doesn't even have to
be true.

The ground is eaten out from beneath us.
We will take Berkeley, Kant and the whole
rout of idealists along to the stars, lured by
worlds we have pre-populated but cannot
reach.

The dream time is upon us.
