\chapter{}

The limitations of the new information languages, the limitations of the machines, storages, operating systems, circuitry, machine-compatible logic, programs diminish what was once far richer. The old words were broader; they packed complexes of implication within them; their ambiguities allowed for richness and latitude, for rethinking, redefinition from time to time. They contain treasuries of implication within them; the \enquote{amounts} of information they contain are staggering. Consider Eliot's \booktitle{The Wasteland}:

How do you represent, in terms of specification, and thus bits of information (if that is even the way to put it) the endless galaxy of implications contained in Eliot's poem? In the first place the poem is a rhythmic index, a memory-system. The allusive and apparently self-contained word or phrase opens up into other poems, and histories. That is to say they are references to memory storages. The first line reads \textquote{April is the cruelest month...} \emph{All} Aprils included; the April of Chaucer, the April/Easter of the crucifixion, \booktitle{The Divine Comedy}, all the Aprils contained in \booktitle{The Golden Bough}, and all the rites of spring, sacrifices and renewals to insure fertility, of dying and being planted in the earth to spring up in a new form. Are we to mix our terms here? For example, political, social, economic conditions, to say nothing of genetic evolutionary and \enquote{adaptive strategies} and continuities to be considered as the stuff of literary concerns\ldots\ at least not \emph{directly}.\footnote{Although the naturalists had tried to meld science into literature.} Nor had passion, hatred, character, conflict, ceremony been allowed to be part of science. But once we consider the universe to be language, information, then fiction and magic permeates it all. When experience and reality are processed by computer, the usual domains and disciplines are mixable. Once discrete realms shatter again, their languages melt, float, interface. Multi-lateral Pythagoreanism. But then, hadn't this modern fusion of realms been anticipated by dreams and surrealism, but in a non-quantified, anti-particleized way?

Agriculture itself as a metaphor for death, all resurrection, and conversely. In ancient thought, of course, the spoken and acted-out rite is a ceremony pre-operational to planting: it is a planning and management system. It \emph{precedes} the actuality of material life, as the modern rite of manipulating the memory of past and future wheat crops inherant in money \emph{precedes} all spring plantings and growths.

There is the question of metaphor and simile, which the computer \emph{cannot} handle unless given specific instructions, and then within a limited set of circumstances (which may grow, but becomes unwieldy). Metaphor is a form of \emph{fused association}, sometimes of completely \emph{unrelated} terms (except in the mind ofa poet, novelist, or advertising copywriter), to create a third term, but in a pecu- liar way. In the world of program-driven computers, one list of items may be matched to another list. What is compared are two or more strings of \emph{stored-up impulses} (given in one or another set of computer languages). Beneath, on the level of circuitry and machine-language, something different happens than thought. \emph{Items are not being compared.}

All items in natural language are not bounded by the compartmentalization required by a computer: they have no true boundaries. Truly different sets of items \emph{cannot} be compared unless a tedious and endless program is written on the order of "if [\![ this \ldots\ ]\!] then [\![ that \ldots\ ]\!]" An algorithm describing the way metaphors are generated can be easily written; it cannot be implemented or generated by a computer language. The instructions could be written such that \enquote{whenever \enquote{April,} then \enquote{cruel}}, but only applies to these terms whenever \enquote{April} and \enquote{cruel} appear. But supposing that another poet appears, working out of another framework, to speak of April in conjunction with the autumns of the southern hemisphere?

In order to unlock the poem's meaning, one already has to have access to a vast knowledge of literary, religious, anthropological, political, historic, mythological and psychological compilations (and those edited) in order to summon up the full text of references. The way the fragments are allusively juxtaposed may be analogized to the way information is stored, organized and sequenced on a disc ... in non-sequential fragments with memory addresses. Well and good.

It may be said that the retrieval process of the brain-body is somewhat like the retrieval process in a computer, but there are significant differences. (That is if anyone knows what goes on in the brain). The computer was orginally likened to the brain. The terms were reversed and the brain was likened to the computer, leading to ridiculous assesments—tried out experimentally—that the brain \enquote{processed} information in an on and off way. Later this was modifed and it was said that the brain \enquote{parallel-processed.} The mental processes are associational and quasi-random, and frequently get confused, yielding felicitous mixes. The computer processes are much more rigid and limited. It is when, in the poem, the fragments are fused that the difference becomes more apparent. The computer cannot fuse associations into a seamless whole.

Fiction, drama, poetry, non-quantifiable psychology and other traditional modes of discourse are partial but stand for wholes; they have long incorporated complex modes of organization of people, events, matter into dramatic sequences ... novels, plays, epics, poems, psychological theories ... Creating indices, hierarchies, queues, maps, models, simulations, translations, sets, classes are some of the problems raised by information handling. Each reorganization raises these problems again and again in new ways.

All literary works contain, among other things, indices and every such work solves the problem of hierarchy, or of queueing without specifically delineating these modes of sorting as problems. Literaure does not accept polarities as absolute oppositions. Dialectics is the emanation of crippled and self-constrained minds ... the realm, really, of accountants. Hierarchy? It's all in Dante. Sets? Borges deals with them wittily. Indexes? See Eliot. In literature (and literary psychology ... such as Freud's or Jung's) all these modes are dynamic, allusive, \emph{multireferential.} As for set-theory, this is, of course, the mathematician's and logician's whimsey. As in life, literature shatters sets.

In real life, all sets are fuzzy. For example; in a complex, transnational, transtemporal holding company which owns other companies and parts of companies and constantly seeks to conceal itself behind a thousand portals represented by the shell-names of companies distributed in a lot of countries, which is the set of all sets? The subsidiary or subset may contain (by control) the set of all sets. In fact, taken all in all, the contiguity of economic (and political) activity eventually links and sends the representations of each part of itself at incredible speeds to every other economic and political body \emph{in the world} these days, especially in the age of advanced telematics. In the modern world, America, France, the USSR (since transnationals overlap their boundaries) ... are indeed fuzzy sets, better expressed in literary language... indeed, the language of \booktitle{Finnegan's Wake}. (And one may say that a set, called for convenience Mafia, is conjoined and interpenetrates those sets called corporations and those sets called governments through other interpretive realms called politics, by using a set-violating, economic activity called bribing... It is, to be sure, primarily and economic organization, but on the other hand, requires primitive rituals as part of its sustaining power.)

The way of the fiction writer and mythmaker is a function of long stores of knowledge, arrayed in certain ways, drawing from a taken-for-granted memory bank. The world of information processing is a world of partial faiths and fictions. Tests for truth that match reality are meaningless in this world: inner consistency is what counts.

In literature (its application to the new information world will soon emerge) one converts the experiences of the self and others into words. (What sensors does one use to acquire the experience of others? Through what set of filters --- ideas, technology, legends, myths, psychological and social theories, artificial memory/intelligence --- does one sift one's own personal experience?) The writer uses imagery, similes, symbols, signs, translations, conversions, comparisons, metaphors, tropes, compact representation, character, emotion, conflict, drama in certain limited situations. All dictated by a body of traditions. Experience, real people, furniture, space, action, geometry, geology, geography are converted into evocative words and are arranged into some new structure, perhaps more neatly --- or more amusingly, or startlingly --- than in life. Fiction, poetry, drama are programs designed to transmit energy which \emph{amplifies} as it goes through its \enquote{circuits.} There is selection. One cannot write about everything.

The compilers and refiners, the preservers and organizers, the abridgers who assembled and trimmed the treasure, the great canon of literature (surely there was always editing and censorship involved), assert that their Great creations represent whole populations ... Man and Woman writ large. But in fact these are \emph{sampling} techniques, which can provisionally be said to have been invented by the Greek Tragedians. But what is left out? Among other things, the living stuff of humans, which involves neuronic, hormonal, enzymatic, chemical, metabolic, genetic, electromagnetic activity had not been fit for literary language. Yet one could come up with a prototypical set of biological reactions accompanying (indeed, initiating and sustaining) mythological, literary and religious prototypes and archetypes.

When Proust bites into the tea-soaked Madeleine, the taste is a stimulus to releasing memory which then pours out and is recorded as a printout. We have a report of Proust's brain operating, but in another language. We could also write a biochemical essay which replicates the event. We could also say that Proust wrote a treatise on information storage and retrieval, on the long and short-term memory, in which the tea-soaked Madeleine is the key word, and the instruction, that begins the memory dump.

When a marketing study is prepared, psychology and sociology is used to create the stimuli, the association of ideas that will generate the \emph{feeling} which reaches the memory to release biochemicals, electrical charges, symbols. All emotions, behaviors, dramas and tastes are tallied, sampled and compared with standardized and representative beings: prototypes, concurrent archetypes: the hypostatic buyer. Frequently life-signs are monitored by biological telemetering equipment. But, at the same time, the marketers must try to turn diverse populations into Standard Consumers; infecting the archetypal consumer's memory with prototypical hunger. Persuasion.

\emph{True} archetypes, \emph{original} archetypes, prototypical figures, their deeds and emotions are communicated down through the ages. From time to time their attributes are altered to adjust to newer ages. These are used as templates to force people into those imageforms. Consider that message called \emph{Oedipus} and how it has been used again and again. But were such recorded, aboriginal events prototypical? Who, what set of people made them that way and why? If Jung talks about the collective unconcious, one must not only ask, \enquote{who collected it?}, but who keeps reminding us? And what are we not reminded of? Who speaks of the archetypal revolutionary, the primal guerrilla?

Some set of \enquote{orginal,} transcribed events and characters are made into standards, broadcast and rebroadcast. Those who follow are made to resonate to the original signal. People through the ages are made into transcievers. The emotion of a perhaps once-lived life in turn gains power to motivate people across time and space. In fact, the people, the transcievers, the relays, are frequently more emotionally moved by these compulsive fictions than by their own life or the people they live among. They are taught to screen their own experience through these long-transmitted stereotypes, reassessing their own lives, comparing, matching, referencing, denying what they are in fact living out, viewing what is around them through mediational scrims.

Some humans, fearing death, watch the butterfly emerge from its chrysalis, or they see the seed planted, going into the winterdead ground, and grow up as grain, and dream of the time when they can metamorphose, transubstantiate into angels and gods. The whole algorithm of agriculture is described in Christian thought, represented by a human\slash divine figure in its metamorphoses into divinity. So they invent varieties of immortality. The way to immortality lies through death; it begins with a dissolution, a liquidation and ends with a reconstruction, recombination, resurrection.

But the progrssive series of deaths and resurrections lead somewhere. (Not \enquote{true} death, for energy and matter are conserved.) If we view the world, the universe in a quantum-operational sense, in which the observor intervenes in the observed, then, as we have said, \enquote{Mind} permeates the universe and must constantly be sustained and reproduced or the universe will cease to exist. Thus, \emph{all} the instruments of perception, of past and present, place mind in the univese and the universe in\slash as\slash of mind. True, the referential frameworks change and the rules change. Thus dreams permeate through skins, flow through all boundaries and are shuttled back and forth in history; empty space becomes a plenum which manifests itself into sometimes virtual entities, fields of particles and waves, sometimes real and permanent entities which are viewed with astonishment. Life is an illusion; the flow, the dance, the perpetuation and evolution of language is all, and bodies lyse into language, symbols, matter, space, velocity, energy, bodies, money... (Perhaps humans resist this liquidity. When humans are converted into economic symbols, one form of capital, the being is liquified, transsubstantiated into capital. What is capital but a set of numbers which will metamorphose again into factories or other humans?) The first law of thermodynamics tells us that matter and energy are conserved. Then the instruments that view these events are also conserved. That is to say mind is eternal. (Really?) And perhaps, so is time. And clearly we can see the whole program of the birth, life and death of the universe speeded up for us in a reconstructive program. But more, we can now populate our computer with a plethora of virtual, interconnecting and concurrent spaces and minds, as the Kaballists had proposed so long ago. Perhaps we will see them, since these fictions will have themselves become instruments of perception.

In the pre-Judeo\slash Christian past, the metamorphoses were circular or cyclical, happening without any purposive, long-range strategy. The Jews and Christians introduced two complementary --- yet opposing --- long-range strategies; non-repeating, goal-oriented history, which led to collective immortality, out of which sprung metaphysical evolution. Events in time were arranged in an ascending sequence leading to collective death, transfiguration, resurrection and escape into paradise ... a reuniting with that from which they had originally been seperated from.

With the advent of the industrial-scientific-technological-capital revolutions, the transformation programs \emph{appeared} to be secular. Events were arranged into a \emph{non-}Judeo\slash Christian, long range strategy of transcendance. \emph{Qualitative}, metaphysical transubstantiation was replaced by an accretive, recombinatorial, technology-assisted march toward transubstantiation (since everything can be prised apart into units, numbered and rearranged). This invention was called progress, though still incorporating the old notions of immortality. At certain stages, the accumulation would reach a critical mass and a quantum leap into a new period would take place. Permanent revolution. This was a reaction to that perpetuated, obsessive dream of a faded paradise, the Roman Empire, and the descent into Feudal chaos. How many expulsions from timeless and non-progressive paradisos haunt our \emph{collected memory}? This kind of thinking led to concepis of rational forecasting, retrocasting, planning, management.

But since events had to be scheduled in a practical, materialistic, exponentially rising line, in order to gain escape-velocity, in order to escape entropic fate, it was clear that man's ascendant journey required a series of engineered metamorphoses. The mechanisms of natural evolution seemed to be gone. And anyway, Man wouldn't let any new form that emerged from him, challenge him. This meant that the journey toward immortality required tapping the earth's and the universe's energy. And if one were to harness the universe's energy, that would cost a lot, and anyway, most people, while fearing death, were not nescessarily interested in immortality: the enterprise had to be sold. Enter \booktitle{Faust}.

\booktitle{Faust} stands for a key word, one of many in a directory of transcendance strategies. \booktitle{The Divine Comedy} is another. \booktitle{Faust} is dynamic and action-oriented: Dante is static. Dante (and The Church) encouraged saving of energy and cutting down of indulgence-expenditure --- called sin --- while Faust encouraged profligacy as a means toward progress.

One general form of the transcendance algorithm runs this way: Hero seeks, or is impelled to seek knowledge; hero has dream, or dies, or passes into another realm; the new, or next world is revealed; hero comes back, or leaves directions in the form of a book. Note the role of knowledge or information.

\booktitle{Faust} is the great poetic myth representing the transition from the medieval to the modern age, from medievalism to capitalism, from agricultural\slash feudal society to industrial (and then to the information society), from one kind of magic to another. (And it is Eliot's lament that we had taken the wrong path.) \booktitle{Faust}'s ascent is built around one concrete and one mystic project. The concrete project involves a dam and land-reclaimation. \booktitle{Faust} is in every marketing strategy the computer and software manufacturers generate. The mystic project is the transubstantiation of, the rejection of the body and the earthly life, earthly events and time, history, and mundane procreation, utilizing a meta-sexual image. \booktitle{Faust} becomes, as it were, one of the programs of modern society. The dependance on mystic knowledge, information, is very strong.
